### 2022-10-21 Manuscripts/deNovoRates.tex
modified:   Manuscripts/deNovoRates.tex

>>>>

Previous studies have argued that hydrophobic amino acids are comprise 40\% of amino acids and can also easily arise due to mutation pressure. They based these conclusions on mutation rate bias estimated in bacteria. We asked if our model also makes similar predictions. To this end we calculated expected hydropathy in a protein sequence, based on expected frequency of different amino acids (\autoref{aafreq}) and their hydropathic index values (Kyte and Doolittle). We found that the expected hydropathy is $-0.08628$, which suggests that random protein sequences are not mostly hydrophobic.

Next, we calculated the probability that any
